Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-21 paper/paper.tex
updated values on sec 3.1

\tname{} proceeds as follows to synthesize rules for this
attack. First, it analyzes the positive (\ie, malicious) traffic and
extracts options expressed in that traffic. In this case, the
malicious traffic is characterized as a sequence of 20
messages. \tname{} finds the following set of options at this stage:

@@

\noindent
\tname{} only reports a rule if the \nids\ instantiated with that rule
is able to capture the traffic passed on input. Consequently, by
construction, a rule that uses this set of options captures the
malicious traffic. Unfortunately, this rule is potentially
overspecified. Informally, the rule includes ``too specific''
characteristics of the malicious traffic and could potentially result
in false negatives. For example, in this particular case, note that
the option \CodeIn{windows: 512} is not included in the golden rule
from Figure~\ref{fig:synflood-example}.

@@

Finally, \tname{} ranks the inferred rules according to heuristics
extracted from a database of existing rules. One example heuristic
function we used to rank the generated rules was
\Fix{...elaborate...}. The list below shows the rule options for the
top-5 rules \tname{} produces for this attack.

\Mar{listem 5 primeira regras neste caso}

@@

\vspace{1ex}
\noindent
\textbf{Differences.}~Note that there are differences between the
options produced in the first step of \tname{} and the options from
the golden rule, as per Figure~\ref{fig:synflood-example}. The option
\CodeIn{flags} does not mention parameters \CodeIn{1 2}, there is an
extra option \CodeIn{window}, and there are differences in the option
\CodeIn{threshold}. Considering the option \CodeIn{flags}, the first
parameter of that option indicates what flags in the packet must be
set while the second parameter indicates non-mandatory flags (\ie{},
``don't cares''). The option \CodeIn{flags: S} indicates that the flag
``S'' must be set and all flags not mentioned (``1'' and ``2'', in our
case) must be unset for the \nids\ to capture the
traffic. Consequently, that choice of option alone could result in
false negatives and false positives. An attack that satisfies all
other conditions in a rule and have flags ``1'' or ``2'' set would be
captured by the original rule but not the inferred rule---a case of
false negative. Likewise, an attack that satisfies all conditions and
have flags ``1'' and ``2'' unset would be captured by the inferred
rule but not the original rule---a case of false positive. The set of
positive examples is to blame in this case. To mitigate this issue,
the input messages should have covered cases with options ``1'' or
``2'' set. Considering option \CodeIn{windows: 64}, \tname{} is able
to generate rules without that option, as discussed above. Considering
option \CodeIn{threshold}, the values used in the golden rule are
domain-specific. \tname{} uses default values for these options. We
conjecture that the system administrator would be able to configure
this option.

@@

\Luc{Apenas 3 regras tiveram f1 de 100\%. O total de regras nesse caso foi de 13.}
\Fix{...listem 5 primeiras regras neste caso...}

>>>>

\tname{} proceeds as follows to synthesize rules for this
attack. First, it analyzes the positive (\ie, malicious) traffic and
extracts options expressed in that traffic. In this case, the
malicious traffic is characterized as a sequence of 5000
messages. \tname{} finds the following set of options at this stage:

@@

\noindent
\tname{} only reports a rule if the \nids\ instantiated with that rule
is able to capture the traffic passed on input. Consequently, by
construction, a rule that uses this set of options captures the
malicious traffic. Unfortunately, this rule is potentially
overspecified. Informally, the rule includes ``too specific''
characteristics of the malicious traffic and could potentially result
in false negatives. For example, in this particular case, note that
the option \CodeIn{window: 512} is not included in the golden rule
from Figure~\ref{fig:synflood-example}.

@@

Finally, \tname{} ranks the inferred rules according to heuristics
extracted from a database of existing rules. One example heuristic
function we used to rank the generated rules was \Luc{a quantidade de opcoes na regra}
\Fix{...elaborate...}. The list below shows the rule options for the
top-5 rules \tname{} produces for this attack.

@@

\vspace{1ex}
\noindent
\textbf{Differences.}~Note that there are differences between the
options produced in the first step of \tname{} and the options from
the golden rule, as per Figure~\ref{fig:synflood-example}. The option
\CodeIn{flags} does not mention parameters \CodeIn{1 2}, there is an
extra option \CodeIn{window}, and there are differences in the option
\CodeIn{threshold}. Considering the option \CodeIn{flags}, the first
parameter of that option indicates what flags in the packet must be
set while the second parameter indicates non-mandatory flags (\ie{},
``don't cares''). The option \CodeIn{flags: S} indicates that the flag
``S'' must be set and all flags not mentioned (``1'' and ``2'', in our
case) must be unset for the \nids\ to capture the
traffic. Consequently, that choice of option alone could result in
false negatives and false positives. An attack that satisfies all
other conditions in a rule and have flags ``1'' or ``2'' set would be
captured by the original rule but not the inferred rule---a case of
false negative. Likewise, an attack that satisfies all conditions and
have flags ``1'' and ``2'' unset would be captured by the inferred
rule but not the original rule---a case of false positive. The set of
positive examples is to blame in this case. To mitigate this issue,
the input messages should have covered cases with options ``1'' or
``2'' set. Considering option \CodeIn{window: 512}, \tname{} is able
to generate rules without that option, as discussed above. Considering
option \CodeIn{threshold}, the values used in the golden rule are
domain-specific. \tname{} uses default values for these options. We
conjecture that the system administrator would be able to configure
this option.

@@

\Fix{...listem 5 primeiras regras neste caso...}
